\plaintitle

### 2016-08-02 drafts/labor/cases.tex
monday

@@

\subsection{The Processes of Making Gig(s) Work}\label{sec:MakingGigsWork}

\cite{olson2014ways}
The HCI community is perhaps most familiar with examples of task--based work such as
99designs,
Amazon Mechanical Turk (AMT),
and increasingly
Uber \& Lyft,
which all allow requesters in various forms to tap into
resources such as
cars,
computers, and above all
``cognitive surplus''
with relative ease
\cite{howe2006rise,DillahuntPromise,storiesIraniSilberman,shirky2010cognitive}.
This insight, that
workers can be geographically distributed and tasks decomposed,
% (especially given careful central management of those workers, discussed later),
has proven remarkably compelling
and an effective fulcrum for leveraging the Internet for highly scalable work
\cite{sensitiveTasks,embracingErrorKrishna}.

>>>>

\subsection{What are the limits of crowdsourcing?}
For more than a decade
research in crowd work has explored ways of expanding the work that crowdsourcing can do by
  identifying challenges to this form of labor,
  overcoming them through novel designs of work--flows and processes,
and repeating the process
\cite[etc\dots]{bernsteinSoylent}.
The question that has emerged
among these researchers and
through the work that they have produced then
has been whether there are limits to crowdsourcing
(and, if so, what bounds them).

In the field of piecework,
the research covering this topic has both explored
a breadth of tasks that might be rendered doable by piecemeal workers
\textit{as well as} longitudinally documented the success of these approaches.

Points to make:
  \begin{itemize}
    \item Blossoming of piecework
    \begin{itemize}
      \item high point: consultants?
      \item most cases: auto workers/etc\dots
      \item worst case: sweatshops (especially in developing nations)
    \end{itemize}
    \item what led to these outcomes?
    \begin{itemize}
      \item ``consultant'' work came out well because the work was complex;
      this made it difficult to turn into a mass market commodity.
      We see consultants ranging skill levels like
      oDesk (implementing modules) to
      Accenture (on--demand teams of consultants).
      \item auto workers,
      working in settings where capital couldn't be moved as easily
      found themselves in the same workspace as a direct
      --- if multi--stepped ---
      result to the benefits of putting people in the same place to consolidate resources.
      Moreover,
      workers had leverage over factory owners as a result of that consolidated capital;
      operating equipment required training.
      \item sweatshop workers fared the worst,
      for reasons that may seem obvious with hindsight.
      Source materials for textiles are easier to ship than mechanical components such as engines,
      making it easier for factories to relocate to developing nations
      (where cost--of--living, and consequently wages, would be lower).
      As wages, CoLAs, and QoL rise, workers begin asking for
      (and later demanding)
      higher wages and better conditions.
      But where the auto workers have leverage,
      textile workers find only a precarious economic balance now tipped by their collective action,
      spurring manufacturers to move to a new locale

    \end{itemize}
  \end{itemize}

\subsection{What forms of work design and worker management are viable?}
\subsection{What will work and the place of work look like for workers?}

@@

\subsection{The Processes of Making Gig(s) Work}\label{sec:MakingGigsWork}
The HCI community is perhaps most familiar with examples of task--based work such as
99designs,
Amazon Mechanical Turk (AMT),
and increasingly
Uber \& Lyft,
which all allow requesters in various forms to tap into
resources such as
cars,
computers, and above all
``cognitive surplus''
with relative ease
\cite{howe2006rise,DillahuntPromise,storiesIraniSilberman,shirky2010cognitive}.
This insight, that
workers can be geographically distributed and tasks decomposed,
% (especially given careful central management of those workers, discussed later),
has proven remarkably compelling
and an effective fulcrum for leveraging the Internet for highly scalable work
\cite{sensitiveTasks,embracingErrorKrishna}.
